% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\Huge \textbf{Björn Westergard}}
	\vspace{.8em}

	3200 16\textsuperscript{th} Street NW, Apt. 504 \ \ {$\cdot$}
	\ \ Washington, D.C. 20010
	\\
	(202) 758-7332\ \ {$\cdot$}
	bjornw@gmail.com {$\cdot$}
	github.com/bwestergard
\end{center}

\begin{center}
	\hrule
	\vspace{-0.4em}
	\subsection*{Experience}
\end{center}

\begin{itemize}
	\parskip=0.1em

        \item[]
	      \headerrow
	      {\textbf{Megaphone (Panoply)}}
	      {\textbf{Washington, D.C.}}
	      \\
	      \headerrow
	      {\emph{Senior Software Engineer}}
	      {\emph{March 2018 -- June 2019}}
	      \begin{itemize*}
	      \item Worked with another engineer to design and implement a new podcast listenership data pipeline that could handle an order of magnitude increase in download volume. Built around Druid (a timeseries database), we also made extensive use of Terraform, Google Dataflow (Apache Beam, Java), and Cloud Functions (Node).
              \item Developed and implemented a method for forecasting podcast downloads by demographic and geographic segment using historical data from aforesaid pipeline, enabling users to estimate advertising inventory months in advance (Node, Flow, Postgres).   
              \item Forked the open source Turnilo project (Typescript) to integrate it with our Ruby on Rails application by means of JSON Web Tokens, such that users could run arbitrary Druid queries within those subsets of the data they were authorized to view.
                \item Added features to our Ruby on Rails application with React and gave brownbag talks on JavaScript best practices.
	      \end{itemize*}
        
	\item[]
	      \headerrow
	      {\textbf{Lanetix}}
	      {\textbf{Arlington, Virginia}}
	      \\
	      \headerrow
	      {\emph{Senior Software Engineer}}
	      {\emph{October 2015 -- January 2018}}
	      \begin{itemize*}
	      	\item Technical lead of a three person team which developed a plugin platform for the flagship logistics CRM product. Built atop AWS Lambda, DynamoDB, SNS and Postgres with a React UI, this system was used to automate business processes for more than a dozen clients.
					\item Named as first inventor on a patent application drafted by Lanetix, Inc. in connection with this work, \textit{Systems and Methods for Data Translation between Non-Homogenous Datastores}.
	      \end{itemize*}

	\item[]
	      \headerrow
	      {\textbf{UrbanStems}}
	      {\textbf{Washington, D.C.}}
	      \\
	      \headerrow
	      {\emph{Senior Software Engineer}}
	      {\emph{April 2015 -- October 2015}}
	      \begin{itemize*}
	      	\item Sole engineer working alongside founders to implement unified inventory, e-commerce, and delivery system with Node, React, Postgres (PostGIS). This system freed the management team to experiment with different delivery mechanisms within and between cities as the business grew.
	      	\item Surveyed academic literature and collaborated with distribution staff to write software suited to the unique operational challenge of offering same-day delivery of a highly perishable good (bouquets).
	      \end{itemize*}

	\item[]
	      \headerrow
	      {\textbf{NGP VAN}}
	      {\textbf{Washington, D.C.}}
	      \\
	      \headerrow
	      {\emph{Software Engineer}}
	      {\emph{July 2011 -- April 2015}}
	      \begin{itemize*}
	      	\item Worked on small team to develop a Node/Backbone/PhantomJS "Advocacy" application by means of which all of one's elected representatives can be contacted through a single form.
	      	\item Major contributor to Social Organizing application (Drupal/Backbone), through which supporters can match Facebook friends to the national voter file enabling clients to micro-target supporters.
	      \end{itemize*}

\end{itemize}

\begin{center}
	\hrule
	\subsection*{Tools}
\end{center}

\begin{indentsection}{\parindent}
	\hyphenpenalty=1000
	\begin{description*}
		\item[Languages:]
		JavaScript, Python, C$^\sharp$, Java, PHP. Limited experience with OCaml, Go, C++, Scheme, Ruby, SuperCollider, Rust.
		\item[Frameworks:] React, Redux, Express, Drupal, Django, Backbone.
		\item[Data Stores:] PostgreSQL (including PostGIS), Druid, MySQL, DynamoDB, MongoDB, Redis.
		\item[DevOps:] AWS (Lambda, SNS, SQS, CloudFormation), Google Cloud (Cloud Functions, Dataflow), Terraform, Babel, Flow, Mocha, CircleCI, Heroku, Webpack, Browserify, Chrome Headless.
	\end{description*}
\end{indentsection}

\begin{center}
	\hrule
	\vspace{-0.4em}
	\subsection*{Education}
\end{center}

\begin{itemize}
	\parskip=0.1em

	\item[]
	      \headerrow
	      {\textbf{Northern Virginia Community College}}
	      {\textbf{Arlington, Virginia}}
	      \\
	      \headerrow
	      {\emph{Courses in Mathematics, Computer Science}}
	      {\emph{2009 -- 2011}}
	      \begin{itemize*}
	      	\item Calculus (3 semesters, through multi-variable), Discrete Mathematics, Linear Algebra
	      	\item Objected Oriented Programming (Java), Assembly (x86), Data Structures
	      	\item Circuits, Digital Design, General University Physics (two semesters)
	      \end{itemize*}

\end{itemize}

\end{document}
